### 2020-08-11 manuscript/explorations/phylobayes_explorations.rmd

  source( "../phylobayes.R" )

@@

@@

plot_chain = function( pb ){

@@

  categories = tibble(
    index = index,
    count = c(allocation_counts),
    x = fit$points[,1],
    y = fit$points[,2]
  )

  gg_mds = 
  categories %>% 
    ggplot() +
    geom_point(aes(x=x, y=y, size=count), alpha=0.4 ) +
    ggtitle("MDS plot of rate categories") +
    theme_classic()

  gg_rank = 
    categories %>%
    arrange(desc(count)) %>%
    mutate(rank = 1:nrow(categories)) %>%
    ggplot() +
      geom_point(aes(x=rank, y=count) ) +
      ggtitle("Ordered count") +
      theme_classic()

@@

plot_chain( pb )

>>>>

  source( "../phylobayes.R" )
  source( "../functions.R" )

@@

  aa = PartitionedMultipleAlignment ("../../data_processed/matrices/Whelan2017_strict.phy", "../../data_processed/matrices/Whelan2017_strict.nex")

  m = as.matrix(aa)
  site_occupancy = colSums(m != "-" ) / nrow(m)

@@

plot_chain = function( pb, site_occupancy ){

@@

  # Calculate the mean occupancy for each site in the original matrix
  occupancy = sapply( index, function(i){
    sites = which( pb@allocation == i  )
    mean( site_occupancy[ sites ] )
  })

  categories = 
    tibble(
      index = index,
      count = c(allocation_counts),
      occupancy = occupancy,
      x = fit$points[,1],
      y = fit$points[,2]
    ) %>%
    arrange(desc(count))

  categories %<>% mutate(rank = 1:nrow(categories))

  gg_mds = 
  categories %>% 
    ggplot() +
    geom_point(aes(x=x, y=y, size=count), alpha=0.4 ) +
    ggtitle("MDS plot of frequency categories") +
    theme_classic()

  gg_rank = 
    categories %>%
    ggplot() +
      geom_point(aes(x=rank, y=cumsum(count)) ) +
      ggtitle("Cumulative sum of sites") +
      theme_classic()

@@

plot_chain( pb, site_occupancy )
